### 2009-06-03 paper.tex
minor edit

% figure produced automatically with simulations/plots.r from simulations/inferred/indiegram.analysis
\begin{figure}[!ht]
  \centering
  % \includegraphics[width=5in]{figs_plos/simulations.pdf}
  \caption{
    \textbf{Dependence of reconstruction accuracy on outgroup branch
      length.}
    We investigated the dependence of structural reconstruction and
    alignment accuracy on outgroup branch length by simulating the
    evolution of three structural RNAs under our model.  The two
    sister species were equidistant from the ancestral sequence, with
    a branch length of 1, corresponding to one expected
    substitution per site in loop sequence.  We allowed the outgroup
    branch length to vary between $[0, 2.5]$.  We divided this interval
    into 25 bins and simulated 25 alignments for each bin.
    Parameters used were $\lambda_l = 0.025$ and $\mu_l = 0.03$ for
    loop sequence and $\lambda_l = 0.007$ and $\mu_l = 0.01$ for stem
    sequence; the probability of a stem insertion was $0.1$.  These
    yielded a mean loop length of 5 bp and a mean stem length of 2.33 bp,
    with $\sim 0.3$ substructure indels per alignment.
    We selected challenging alignments to reconstruct by requiring
    that there be at least two ancestral stems, loops of length $\in [3,
    10]$ bp and stems of length $\in [1, 20]$ bp; to reduce the complexity of
    our algorithms we additionally required that the sequences have
    lengths $\in [30, 70]$ bp.
    ``Structural reconstruction accuracy'' is the fraction of
    base-pairs in the ancestral structure present in the
    maximum-likelihood reconstruction thereof; ``Alignment accuracy''
    is a measure of sequence alignment accuracy which takes both
    aligned and unaligned (indels) nucleotides into account,
    qualitatively corresponding to giving equal weight to sensitivity
    and specificity (see
    \cite{SchwartzMyersPachter2006} for a precise definition).
}
  \figlabel{simulations}
\end{figure}

>>>>

% figure produced automatically with simulations/plots.r from simulations/inferred/indiegram.analysis
\begin{figure}[!ht]
  \centering
  % \includegraphics[width=5in]{figs_plos/simulations.pdf}
  \caption{
    \textbf{Dependence of reconstruction accuracy on outgroup branch
      length.}
    We investigated the dependence of structural reconstruction and
    alignment accuracy on outgroup branch length by simulating the
    evolution of three structural RNAs under our model.  The two
    sister species were equidistant from the ancestral sequence, with
    a branch length of 1, corresponding to one expected
    substitution per site in loop sequence.  We allowed the outgroup
    branch length to vary between $[0, 2.5]$.  We divided this interval
    into 25 bins and simulated 25 alignments for each bin.
    Parameters used were $\lambda_l = 0.025$ and $\mu_l = 0.03$ for
    loop sequence and $\lambda_l = 0.007$ and $\mu_l = 0.01$ for stem
    sequence; the probability of a stem insertion was $0.1$.  These
    yielded a mean loop length of 5 bp and a mean stem length of 2.33 bp,
    with $\sim 0.3$ substructure indels per alignment.
    We selected alignments to reconstruct by requiring
    that there be at least two ancestral stems, loops of length $\in [3,
    10]$ bp and stems of length $\in [1, 20]$ bp; to reduce the complexity of
    our algorithms we additionally required that the sequences have
    lengths $\in [30, 70]$ bp.
    ``Structural reconstruction accuracy'' is the fraction of
    base-pairs in the ancestral structure present in the
    maximum-likelihood reconstruction thereof; ``Alignment accuracy''
    is a measure of sequence alignment accuracy which takes both
    aligned and unaligned (indels) nucleotides into account,
    qualitatively corresponding to giving equal weight to sensitivity
    and specificity (see
    \cite{SchwartzMyersPachter2006} for a precise definition).
}
  \figlabel{simulations}
\end{figure}
